Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-04-10 Reviews/response.tex

\begin{quote}
    \begin{textit}{
    On page 5, the model is referred to as a Figure 6. This confuses and leaves a question on whether it is a figure or equations. I am unsure whether figure 6 is missing or authors are referring to the model on page 6.
    }\end{textit}
\end{quote}

This has now been fixed: the optimisation problem that defines the game is now
in a section with title: `Optimisation problem' and is referred to by a
labelling equation number. This was suggested by another reviewer and we feel
improves the paper.

\begin{quote}
    \begin{textit}{
The paper is unreadable. The unknowns used, some, are undefined, for example on page 3, h, ch, etc are not defined and it is very difficult to find definitions of those defined. I suggest that the authors provide a list of the parameters used somewhere in the paper where it is easy to refer.
    }\end{textit}
\end{quote}

We were disappointed by this comment. Page 2 contains a table that clearly
lists the variables.

If we have misunderstood and that table is not sufficient, we would gladly list
the variables with their definitions in a format more pleasing to the referee.

@@

``
It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure 12. This is potentially due to the fact that as demand increases there is the scope for larger discrepancy between optimal and sub optimal behaviours.
''

\begin{quote}
    \begin{textit}{
    Are the Queuing and Game theoretic models never been implemented to solve such problems? There is a need to review literature that has information on application of the used models to hospital problems or related problems.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
The authors need to give a justification on the reason why they are implementing the models.
    }\end{textit}
\end{quote}

As highlighted by the 3rd reviewer a literature review is present. This
literature review highlights that there is not much work at the intersection of
game theory, queueing theory and healthcare.

Furthermore the contributions and goals of the model are clearly stated on page
2 and again highlighted in the conclusion section. If the reviewer could
clarify expectations if this is not sufficient, we would gladly highlight the
contributions of the paper further.

@@

\begin{quote}
    \begin{textit}
        {I recommend that the authors write a more complete and coherent
        Discussion and/or Conclusion which places their work in the context of
        the critcal care system.  It should relate model limitations to the
        critical care system. The current way that limitations are discussed
        is too technical. A brief discussion of stakeholder feedback would
        also be useful.}
    \end{textit}
\end{quote}

This has been addressed, each technical bullet point is now complemented by a
sentence putting the limitation in the context of critical care. Furthermore a
discussion has been added that describes the feedback and further emphasises the
contribution of the work:

``
Despite these mathematical limitations the work presented here gives a strong
analytical evidence as to the use of policies in a decentralised healthcare
environment.

As discussed above, reducing the decision making of critical care managers to
rational reactions to capacity targets is not without limitations. However, this
quantitative model of behaviour was described as insightful and informative by
ABUHB. In practice, stakeholders describe a target of 80\% capacity. Whilst this
is not only at times impossible it is also not evidence based and in particular
does not take in to account interactions between CCUs. This is a common theme in
practice and the literature which this manuscript aims to address.
''

@@

\begin{quote}
    \begin{textit}
        {
        At the beginning of Section 3.1, the authors claim that if neither CCU
        is able to admit patients, then admission to the CCU is cancelled and
        the patient is admitted to a general ward. In my experience modelling
        CCUs, it is highly unlikely that a critical patient would ever be
        admitted to a general ward.  CCU beds are almost always equipped with
        ventilators and ward beds never. I believe that more likely courses of
        action are:
        \begin{itemize}
         \item Sending the patient to another hospital's CCU.  This would be a CCU
           outside of the model.
         \item ``Bumping" a patient currently in the CCU to a ward bed, to free up
           a bed. This would normally be a patient who was nearly ready to be
           transferred to the ward anyway.
         \item Accommodating the patient in the hospital's post-anesthesia care
           unit (PACU), which sometimes functions as an overflow for the CCU.
        \end{itemize}
        I recommend that the authors consult with their stakeholders and
        correct this comment in their paper, if necessary.  This wouldn't have
        any impact on their model, but it is important to use the correct
        language.
        }
    \end{textit}
\end{quote}

This is a very good point, after discussion with our stakeholders we confirm all
the suggestions made by the reviewer and have modified the text:

``
This model assumes that if the bed occupancy level at both CCUs exceeds a
predetermined threshold, then the admission to the CCU is cancelled. This
cancellation could correspond to sending the patient to a completely different
CCU (outside of the model), moving one of the current CCU patients (ready to be
discharged) to another ward and/or using the post-anesthesia care unit
as a temporary overflow measure. This models corresponds to the first of those
possibilities: the patient is lost (from the point of view of this model).
''

@@

\begin{minted}[frame=lines]{python}
capacity_list = [2, 3]
serviceratelist = [0.22, 1.66]
demandratelist = [3, 1]
model = Model2(capacity_list, serviceratelist, demandratelist)
model.sweepcutoffs()
tps = {model.data[pair].throughput1 + model.data[pair].throughput2: pair for pair in model.data}
for tp in sorted(tps.keys()):
    print round(tp,6), tps[tp]
\end{minted}

A brief discussion of this has been added to the paper which now reads:

``
... This optimal throughput \(T^*\) is
independent of \(t\).

Note that intuitively it could be thought that \(T^*\) is obtained when
\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\); however this is not always the case
(numerical experiments have been carried out to verify this).
''

### 2016-04-10 Paper/paper.tex
Update response following comments by JG and IS
Also fixing paper where relevant.

This model assumes that if the bed occupancy level at both Units exceeds a
predetermined threshold, then the admission to the CCU is cancelled. This
cancellation could correspond, to sending the patient to a completely different
CCU (outside of the model), moving one of the current patients (ready to be
dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
as a temporary overflow measure. This models corresponds to the first of those
possibilities: the patient is lost (from the point of view of this model).

@@

As discussed above, reducing the decision making of critical care managers to
rational reactions to capacity targets is not without limitations. However, this
quantitative model of behaviour was described as insightful and informative by
ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
is not only at times impossible it is also not evidence based and in particular
does not take in to account interactions between CCUs. This is a common theme in
practice and the literature which this manuscript aims to address.

>>>>

This model assumes that if the bed occupancy level at both CCUs exceeds a
predetermined threshold, then the admission to the CCU is cancelled. This
cancellation could correspond to sending the patient to a completely different
CCU (outside of the model), moving one of the current CCU patients (ready to be
discharged) to another ward and/or using the post-anesthesia care unit
as a temporary overflow measure. This models corresponds to the first of those
possibilities: the patient is lost (from the point of view of this model).

@@

As discussed above, reducing the decision making of critical care managers to
rational reactions to capacity targets is not without limitations. However, this
quantitative model of behaviour was described as insightful and informative by
ABUHB. In practice, stakeholders describe a target of 80\% capacity. Whilst this
is not only at times impossible it is also not evidence based and in particular
does not take in to account interactions between CCUs. This is a common theme in
practice and the literature which this manuscript aims to address.
